Metal Mixing in Dwarf Galaxies is Dependent on Nucleosynthetic Source

### 2018-07-15 main.tex
Update on Overleaf.

We show in Figure~\ref{fig:log-normal} the numerical PDFs (solid histograms) and log-normal + power-law fits (dashed lines) across individual gas phases. These PDFs have been computed at an arbitrary single point in time, at 380 Myr. For clarity, we only show a subset of the 15 elements we follow. As shown, there are clear differences in the PDFs across elements of different nucleosynthetic origins and between each phase. However, each of these distributions are characterized by a power-law tail towards high metal fractions and a turnover of varying width at low metal fractions. We discuss the differences among each phase in more detail in the next section, but note here that the significance of each of these components varies notably across phases. In many of these cases, the piecewise log-normal + power-law distribution fits the numerical PDF quite well. However, there are often deviations, particularly at low metal fractions, from pure log-normal behavior. This manifests as either a very broad, flat PDF at low metal fraction (see N and Ba, for example), or large peaks not well described by $p(Z)$ at low metal fraction. In these situations, it is unclear what, if any, portion should be considered as a log-normal, or if there are multiple components within this region.

@@

Unfortunately, there is insufficient star forming gas at any one time in these simulations to construct a PDF of metal distributions. However, star forming gas originates from the CNM, so it is reasonable to expect that this gas, and therefore stars themselves, follow a similar PDF to the CNM. To verify this, Figure ~\ref{fig:stars} shows the difference between the mass fraction of a given element in stars and the median mass fraction from the CNM PDF at the time that particle formed. Stars seem to be sampled evenly around the median of the CNM distribution (i.e. there is no obvious bias towards high metal fractions). Additionally, if we further subdivide the CNM by density, the metal fraction PDFs narrow and tend towards the median value as a function of increasing density. High density gas, from which star formation occurs, is not biased towards higher metallicity in cold gas.

>>>>

We show in Figure~\ref{fig:log-normal} the numerical PDFs (solid histograms) and log-normal + power-law fits (dashed lines) across individual gas phases. These PDFs have been computed at an arbitrary single point in time, at 270 Myr. For clarity, we only show a subset of the 15 elements we follow. As shown, there are clear differences in the PDFs across elements of different nucleosynthetic origins and between each phase. However, each of these distributions are characterized by a power-law tail towards high metal fractions and a turnover of varying width at low metal fractions. We discuss the differences among each phase in more detail in the next section, but note here that the significance of each of these components varies notably across phases. In many of these cases, the piecewise log-normal + power-law distribution fits the numerical PDF quite well. However, there are often deviations, particularly at low metal fractions, from pure log-normal behavior. This manifests as either a very broad, flat PDF at low metal fraction (see N and Ba, for example), or large peaks not well described by $p(Z)$ at low metal fraction. In these situations, it is unclear what, if any, portion should be considered as a log-normal, or if there are multiple components within this region.

@@

Unfortunately, there is insufficient star forming gas at any one time in these simulations to construct a PDF of metal distributions. However, star forming gas originates from the CNM, so it is reasonable to expect that this gas, and therefore stars themselves, follow a similar PDF to the CNM. To verify this, Figure ~\ref{fig:stars} shows the difference between the oxygen mass fraction of stars and the median mass fraction from the CNM PDF at the time that particle formed. The large scatter at early times ($<$ 120~Myr) is a result of the early enrichment phase, when the initial gas oxygen mass fraction was zero. Stars seem to be sampled evenly around the median of the CNM distribution, with only a slight bias (52\% of stars) towards values below the median. However, for stars formed after the initial phase, the median separation from the CNM median is 0.31~dex, and can reach up to $\sim$~0.5~dex. Though a significant deviation, this is smaller than the typical IQR of the CNM (see Figure~\ref{fig:phase-statistics}). Additionally, if we further subdivide the CNM by density, the metal fraction PDFs narrow and tend towards the median value as a function of increasing density. High density gas, from which star formation occurs, is not biased towards higher metallicity in cold gas.

The first core collapse supernova occurs at 12~Myr,

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{stellar_CNM_distance.png}
\caption{The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the within 1~Myr (our time resolution) of each star's formation time. The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
\label{fig:stars}
\end{figure}
